\textbf{Computational Fuzzy Extractors}

### 2013-06-20 CompFuzzExt.tex
notation and explanations changed in 4.1, 4.2 and C.4

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\textbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}

@@

\begin{construction}
Let $n$ be a security parameter and let $m> n$\bnote{should we just switch to $m\ge 3n$ here?}.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\decode_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{B}=\vect{C}-w'$.
\item Let $X = \decode_t(\vA, \vect{B})$\\
\item Output $r = X_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

@@

\subsection{Security of \consref{cons:informal construction}}
\label{subsec:LWE}
The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a positive integers $n, m$,  a prime $q$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ \bnote{only two places we use this notation.}be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$. 
%The Learning With Errors ($\lwe$) is defined as follows: given access to the oracle that outputs a sample from the distribution $A_{\vx, \chi}$ for a uniform $\vx$, and output $\vx$ with high probability.

\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime (unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding)\bnote{does this belong in a definition?}. The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ \bnote{only two places we use this notation.} for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.

@@

 Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as stated in the following proposition.
%The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
%Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
%We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):

\begin{proposition} 
\bnote{Why is this not a theorem?  For example Theorem 1 from Reg05?}
\label{assume:entropy LWE}
Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$.  Let $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.  If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho}$ is secure.

%H^{\unp}_{\epsilon, s_{sec}}(X | \vA, \vA X+E) =H^{\unp}_{\epsilon, s'_{sec}}(E| \vA, \vA X+E) \geq n\log q $ for $s'_{sec}\approx s_{sec}$.  
\end{proposition}

The above formulation of $\LWE$ requires the error term to come from the discretized Gaussian distribution, which makes it difficult to use it for constructing fuzzy extractors (because using $w$ and $w'$ to sample Gaussian distributions will increase the distance between the error terms and/or reduce their entropy).
%\subsection{LWE with uniform errors}
%\label{subsec:LWE uniform error}
Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ when errors come from the uniform distribution over a small interval (assuming the security of $\LWE$ when errors come from the discretized Gaussian\bnote{Their reduction is ultimately to the same problems not to Gaussian LWE}\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.  The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}).  This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.  The size of these blocks is dictated by the following result of D\"{o}ttling and M\"{u}ller-Quade:
%As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.  
%We present the formulation of D\"{o}ttling and M\"{u}ller-Quade: 
%\begin{lemma}~\protect{~\cite[Theorem 5]{dottling2012}}
%\label{lem:uniform LWE}
%Let $n$ be a security parameter.  Let $q = q(n))$ and $m = m(n) = \poly(n)$ be integers.  Let $\rho = \rho(n) \in (0,1)$ be such that $\rho q\geq 2n^2m$.  Assume there exists a PPT-algorithm that solves the LWE decision problem where $\vA,X$ are drawn uniformly at random and $E$ is drawn from the interval $[-\rho q, \rho q]$ with non-negligible probability.  Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{5/2}m/\rho)$ in the worst case.
%\end{lemma}

%This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
\begin{lemma}~\protect{~\cite[Corollary 1]{dottling2012}}
\label{lem:uniform LWE decision}
Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime and $m = m(n) = \poly(n)$ be an integer with $m\ge 3n$. Let $\sigma \in (0, 1)$ be an arbitrarily small  constant and let $\rho=\rho(n)\in (0,1/10)$ be such that $\rho q \geq 2n^{1/2+\sigma}m$. If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard within a factor of $\tilde{O}(n^{1+\sigma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$,  $\distLWE_{n, m, q, \chi}$ is secure.
\end{lemma}

To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits\bnote{Do we need to cite anything about hardcore?}.  The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.  We state their result for a general error distribution~(noting that their proof does not depend on the error distribution):
\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
\label{lem:many hardcore bits}
 If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure then
\[\delta^ {\mathcal{D}_{s_{sec'}}} ((X_{1,\dots, k}, \vA, \vA X+\chi) , (U, \vA, \vA X+\chi)) \le \epsilon\,,\]
where $U$ denotes the uniform distribution over $\Fq^k$,  $\vA$ denotes the uniform distribution over $\Fq^{m\times n}$, $X$ denotes the uniform distribution over $\Fq^n$, $X_{1,\dots, k}$ denote the first $k$ coordinates of $x$, and $s_{sec}' \approx s_{sec} - n^3$.
\end{lemma}

@@

\subsection{Efficiency of \consref{cons:informal construction}}
\label{sec:time main construction}
%\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
\consref{cons:informal construction} is only useful if $\decode_t$ can be efficiently implemented.  We need a decoding algorithm for a random linear code with $t$ errors that runs in polynomial time.  We present a simple $\decode_t$.  An improved decoding algorithm can replace our algorithm, which will increase our correcting capability and improve \consref{cons:informal construction}.

\begin{construction}
\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
\begin{enumerate}
\item Input $\vA , \vB = \vA X + W - W'$
\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
\item Restrict $\vA, \vB$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, \vB_{i_1,...,i_{2n}}$.
\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
If no such rows exist go to step (2).
\item Denote by $\vA', \vB'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vB_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  
\item If $\vB- \vA X'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $X'$.
\end{enumerate}
\end{construction}

Each step is computable in time $O(n^3)$. 
For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $W$ and $W'$ agree on those rows), and $\vA_{i_1,...,i_{2n}}$ has rank  $n$.  If this happens, then $X'=X$, and the algorithm terminates.  However, we also need to ensure correctness: we need to make sure that if $X'\neq X$, we detect it in step 6.  This detection will happen if $B-\vA X' = \vA (X-X')+(W-W')$ has more than $t$ nonzero coordinates.  It suffices to ensure that $\vA (X-X')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $W-W'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.

Setting $t = O(\frac{m}{n}\log n)$ is sufficient to ensure efficiency.    Random linear codes have distance at least $O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$ (the exact statement is in \corref{cor:code high distance}), so this also ensures correctness.
The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
\label{lem:i t poly time}
%Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$. 
Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.  Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$ (the expectation is taken over the input distribution\bnote{this needs to be more precise} $\vA, \vA X+W - W'$).  It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$).
\end{lemma}
\textbf{Note:}
Even though we are correcting $O(\log n)$ errors, this corresponds to a super polynomial number of possible error patterns; the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns. Furthermore, if we consider the setting of $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3)$ field operations (this does not immediately follow from \lemref{lem:i t poly time}, but requires a simple reanalysis).  Our main theorems get  better parameters when  $t\leq m/n-2$.

@@

\begin{theorem}
\label{thm:lossless secure extractor log}
Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.    Let $d<c$ be a positive constant \bnote{need to describe $d$} and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.  Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c/d+2)n}=O(n)$.  If GAPSVP and SIVP are hard to approximate within polynomial factors% \lnote{removed (on lattices of dimension $n/4$)}  
using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}; efficiency follows by \lemref{lem:i t poly time}. For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  %In particular, we describe how to set $q = \poly(n)$.  
\end{proof}

@@

In contrast, our approach does not require the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ to  be high enough for a computational extractor. Instead, we require that $w$ is not computationally recoverable  given $p$.  This requirement is weaker.  The key difference in our approach is that instead of extracting from $w$, we hide secret randomness using $w$. Computational extractors are not allowed to have private randomness \cite[Definition 3]{krawczyk2010cryptographic}.

The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the error-tolerance $t$.  Our codes (namely, random linear codes) can tolerate higher $t$ than can be efficiently decoded.  In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$\bnote{this sentence worries me a little}.  In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes.

@@

\thref{thm:blockLWE} holds for an arbitrary error distribution~(not just uniform error) in the following sense.  Let $\chi$ be an arbitrary error distribution.  Define $\chi'$ as the distribution where $m$ dimensions are sampled according to $\chi$ and the remaining dimensions have some fixed error.  Then, security of $\distLWE_{n, m, q, \chi}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi'}$.

>>>>

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}

@@

\begin{construction}
Let $n$ be a security parameter and let $m\ge n$.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\decode_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, \vx\in\Fq^n$ uniformly.
\item Compute $p = (\vA, \vA \vx+w)$, \\\ $r = \vx_{1,...,n/2}$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $p$ as $(\vA, \vect{c})$; let $\vb=\vect{c}-w'$.
\item Let $x = \decode_t(\vA, \vb)$\\
\item Output $r = x_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

@@

\subsection{Security of \consref{cons:informal construction}}
\label{subsec:LWE}
The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." We now recall the definition of the decisional version of the problem.

\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}
Let $n$ be a security parameter.  
Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime\footnote{%
Unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding.}.
%
Let $\vA$ be the uniform distribution over  $\Fq^{m\times n}$, $X$ be the uniform distribution over $\Fq^n$ and $\chi$ be an arbitrary distribution on $\Fq^m$.
 The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish the distribution
$(\vA, \vA X+\chi)$ from
 the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.

@@

 Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as follows.
Let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$, where $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.  If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho^m}$ is secure.

The above formulation of $\LWE$ requires the error term to come from the discretized Gaussian distribution, which makes it difficult to use it for constructing fuzzy extractors (because using $w$ and $w'$ to sample Gaussian distributions will increase the distance between the error terms and/or reduce their entropy).
%\subsection{LWE with uniform errors}
%\label{subsec:LWE uniform error}
Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$, under the same assumptions, when errors come from the uniform distribution over a small interval\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.  The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.  This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.  The size of these blocks is dictated by the following result of D\"{o}ttling and M\"{u}ller-Quade:
%As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.  
%We present the formulation of D\"{o}ttling and M\"{u}ller-Quade: 
%\begin{lemma}~\protect{~\cite[Theorem 5]{dottling2012}}
%\label{lem:uniform LWE}
%Let $n$ be a security parameter.  Let $q = q(n))$ and $m = m(n) = \poly(n)$ be integers.  Let $\rho = \rho(n) \in (0,1)$ be such that $\rho q\geq 2n^2m$.  Assume there exists a PPT-algorithm that solves the LWE decision problem where $\vA,X$ are drawn uniformly at random and $E$ is drawn from the interval $[-\rho q, \rho q]$ with non-negligible probability.  Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{5/2}m/\rho)$ in the worst case.
%\end{lemma}

%This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
\begin{lemma}~\protect{~\cite[Corollary 1]{dottling2012}}
\label{lem:uniform LWE decision}
Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime and $m = m(n) = \poly(n)$ be an integer with $m\ge 3n$. Let $\sigma \in (0, 1)$ be an arbitrarily small  constant and let $\rho=\rho(n)\in (0,1/10)$ be such that $\rho q \geq 2n^{1/2+\sigma}m$. If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard within a factor of $\tilde{O}(n^{1+\sigma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]^m$,  $\distLWE_{n, m, q, \chi}$ is secure.
\end{lemma}

To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has simultaneously many hardcore bits.  The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.  We state their result for a general error distribution~(noting that their proof does not depend on the error distribution):
\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
\label{lem:many hardcore bits}
 If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure then
\[\delta^ {\mathcal{D}_{s_{sec'}}} ((X_{1,\dots, k}, \vA, \vA X+\chi) , (U, \vA, \vA X+\chi)) \le \epsilon\,,\]
where $U$ denotes the uniform distribution over $\Fq^k$,  $\vA$ denotes the uniform distribution over $\Fq^{m\times n}$, $X$ denotes the uniform distribution over $\Fq^n$, $X_{1,\dots, k}$ denote the first $k$ coordinates of $x$, and $s_{sec}' \approx s_{sec} - n^3$.
\end{lemma}

@@

\subsection{Efficiency of \consref{cons:informal construction}}
\label{sec:time main construction}
%\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
\consref{cons:informal construction} is useful only if $\decode_t$ can be efficiently implemented.  We need a decoding algorithm for a random linear code with $t$ errors that runs in polynomial time.  We present a simple $\decode_t$ that runs in polynomial time and can correct
correcting $O(\log n)$ errors (note that this corresponds to a superpolynomial number of possible error patterns).
This algorithm is only a proof of concept, and neither the algorithm nor its analysis have been optimized for constants. An improved decoding algorithm can replace our algorithm, which will increase our correcting capability and improve \consref{cons:informal construction}.

\begin{construction}
\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
\begin{enumerate}
\item Input $\vA , \vb = \vA \vx + w - w'$
\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
\item Restrict $\vA, \vb$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, \vb_{i_1,...,i_{2n}}$.
\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
If no such rows exist, output $\perp$ and stop.
\item Denote by $\vA', \vb'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vb_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $\vx' = (\vA')^{-1}\vb'$.  
\item If $\vb- \vA \vx'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $\vx'$.
\end{enumerate}
\end{construction}

Each step is computable in time $O(n^3)$. 
For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $w$ and $w'$ agree on those rows).  If this happens, and $\vA_{i_1,...,i_{2n}}$ has rank  $n$ (which is highly likely), then $\vx'=\vx$, and the algorithm terminates.  However, we also need to ensure correctness: we need to make sure that if $\vx'\neq \vx$, we detect it in step 6.  This detection will happen if $\vb-\vA \vx' = \vA (\vx-\vx')+(w-w')$ has more than $t$ nonzero coordinates.  It suffices to ensure that $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $w-w'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.

Setting $t = O(\frac{m}{n}\log n)$ is sufficient to ensure efficiency.    Random linear codes have distance at least $O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$ (the exact statement is in \corref{cor:code high distance}), so this also ensures correctness.
The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
\label{lem:i t poly time}
%Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$. 
Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.  Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$~(this expectation is over the choice of random coins of $\decode_t$, regardless of the input, as long as $\dis(w, w')\le t$).  It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$ and random choices made by $\decode_t$).
\end{lemma}

@@

\begin{theorem}
\label{thm:lossless secure extractor log}
Let $n$ be a security parameter and let the number of errors $t = c\log n$ for some positive constant $c$.    Let $d$ be a positive constant (giving us a tradeoff between running time of $\rep$ and $|w|$). Consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.  Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c/d+2)n}=O(n)$.  If GAPSVP and SIVP are hard to approximate within polynomial factors% \lnote{removed (on lattices of dimension $n/4$)}  
using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}; efficiency follows by \lemref{lem:i t poly time}. For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  %In particular, we describe how to set $q = \poly(n)$.  
\end{proof}

@@

In contrast, our approach does not require the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ to  be high enough for a computational extractor. Instead, we require that $w$ is not computationally recoverable  given $p$.  This requirement is weaker---in particular, in our construction, $w$ may have no information-theoretic entropy conditioned on $p$.  The key difference in our approach is that instead of extracting from $w$, we hide secret randomness using $w$. Computational extractors are not allowed to have private randomness \cite[Definition 3]{krawczyk2010cryptographic}.

The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the error-tolerance $t$.  In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes, because decoding algorithms will not reach the information-theoretic decoding radius.

@@

\thref{thm:blockLWE} also holds for an arbitrary error distribution~(not just uniform error) in the following sense.  Let $\chi$ be an arbitrary error distribution.  Define $\chi'$ as the distribution where $m$ dimensions are sampled according to $\chi$ and the remaining dimensions have some fixed error.  Then, security of $\distLWE_{n, m, q, \chi}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi'}$.
